### 2016-09-07 notions.tex
no message

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
and assume that for some $q' \leq q+1$ and $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries (note that without loss of generality
we may assume $A$ always makes exactly $q'$ queries) such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
With probability at least
$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{It is unclear whether the above is tight, but it is also unclear whether
that is something worth thinking about. }

>>>>

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
some $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
(Note that
we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
With probability at least
$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{It is unclear whether the above is tight, but it is also unclear whether
that is something worth thinking about.}
\jnote{I guess the most interesting(?)\@ case for comparison purposes
is when $r=1$. Then one can have a scheme, say, where every query is independently
answered incorrectly with probability~$\epsilon$. Such a
scheme will be $(t,q,\epsilon)$-NY-correct
for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
under our correctness definition (for $r=1$). So the theorem is tight for $r=1$.}
